%%
%
% Aarvay's Resume
% @author Vignesh Rajagopalan <vignesh@campuspry.com>
% Last Modified: 4-9-2011
%
%%

\documentstyle[hyperref, margin, line]{res}
\hypersetup{backref, colorlinks=true, backref, urlcolor=blue,}

 \oddsidemargin -.6in
 \evensidemargin -.6in

 \addtolength{\topmargin}{-.5in}
 \addtolength{\textheight}{1in}

\textwidth=6.0in \itemsep=0in
\parsep=0in

\newenvironment{list1}{
	\begin{list}{\ding{113}}{%
		\setlength{\itemsep}{0in}
      	\setlength{\parsep}{0in} \setlength{\parskip}{0in}
      	\setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      	\setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  	\begin{list}{$\bullet$}{%
      	\setlength{\itemsep}{0in}
      	\setlength{\parsep}{0in} \setlength{\parskip}{0in}
      	\setlength{\topsep}{0in} \setlength{\partopsep}{0in}
     	\setlength{\leftmargin}{0.2in}}}{\end{list}}

\renewcommand{\namefont}{\Huge\textsf}

\begin{document}
	\sffamily
	 \name{Vignesh Rajagopalan \vspace*{.1in}}
	
	\begin{resume}
		\section{\sc Contact Information}
			\vspace{.05in}
			\begin{tabular}{@{}p{2in}p{4in}}
				DF-94, Mega Hostel   & {\it Phone:}  +91 9884 960 659 \\
				SASTRA University, Thanjavur & {\it E-mail:} \href{mailto:vignesh@campuspry.com}{vignesh@campuspry.com}\\
				India  & {\it www:} \href{http://aarvay.in}{http://aarvay.in} \\
			\end{tabular}
		
		\section{\sc Areas of \\Interest}
			\begin{list2}
				\item[-] Data Structures and Algorithms
		 		\item[-] Graph Theory
		 		\item[-] Semantic Web
		 		\item[-] Machine Learning
			\end{list2}
		
		\section{\sc Education}
			{\bf \textsf{SASTRA University}}, Thanjavur, India\\
			\vspace*{-.1in}
			\begin{list1}
				\item[] B.Tech., Computer Science and Engineering, 2009 - present.
			\end{list1}			
			{\bf \textsf{P. S. Senior Secondary School}}, Chennai, India\\
			\vspace*{-.1in}
			\begin{list1}
				\item[] General Schooling/High School, 1994 - 2009.
			\end{list1}
		
		\section{\sc Achievments}
			\begin{list2}
				\item \textbf{\textsf{Winner}} at various Programming events, including technical fests at various universities.
				\medskip
				\item Co-Developed Mobile App \emph{Astrologic} - \textbf{\textsf{Top Recommended}} in Nokia OVI Store - \\\textbf{\textsf{90,000+ downloads}} from over 115 countries.
				\medskip
				\item \textbf{\textsf{Best Project of the Year '09}} in High School for developing a full fledged chat server that runs on my own protocol.
				\medskip
				\item \textbf{\textsf{Ranked No.2}} in \emph{Launch Attack}, an ethical hacking contest conducted by McAfee at NIT Trichy.
				\medskip
				\item \textbf{\textsf{Top Finalist}} in Yahoo Open Hack India, 2011.
			\end{list2}
		
		\section{\sc Work \\Experience}
			{\bf \textsf{FundsIndia Pvt Ltd.}}
			 
			 \vspace{-.3cm}
			{\em Software Engineer Intern} \hfill May, 2011 - Jul, 2011\\
			Worked on the core online portal. Made it more viral by adding few usecases. 
			Wrote a Facebook App to socialize the platform and an API to support interactions between the platform and the app. 
			Wrote a fully customized parser to scrape a source and API(ze) the output into a neat JSON object.
			
			{\bf \textsf{AstroLogic}}		
		 	
		 	\vspace{-.3cm}
			{\em Server-Side Engineer} \hfill Dec, 2010 - Feb, 2011\\
			Took care of the Server-Side scripting and Facebook Application.

		\section{\sc Research \\Experience}
			\begin{list2}
				\item R. Vignesh, S. Vidya Sagar, Karthik Prashanth, \emph{Context Analysis from Social Networks: A Robust Method to Identify Permanent and Current Interests} \qquad (unpublished)
				\medskip
				\item G. Sanjith, R. Vignesh, \emph{On studying interactions in Online Social Networks} \qquad (unpublished)
			\end{list2}
		
		\section{\sc Personal \\Projects}	
			\begin{list2}
				\item \emph{Co-founded} \href{http://campuspry.com} {\textbf{\textsf{Campuspry Labs}}} -- A 100\% hacker-friendly early-stage startup. We work on building awesome products.
				\medskip
				\item \emph{Co-developed} \textbf{\textsf{AstroLogic}} -- A reasonably popular Astrology/Horoscope application developed for both J2ME and Facebook Platforms.
				\begin{list2}
					\item[-] It became the \emph{Top Recommended} app at the Nokia OVI Store in the first week of it's launch.
					\item[-] Got over 90,000+ downloads, from 115 countries.
				\end{list2}
				\medskip
				\item \emph{Developed} an \textbf{\textsf{Online Quiz Portal}} for \emph{IBM's Bluebattle}.
				\begin{list2}
					\item[-] Includes features like timed snap out, randomizing questions, and grading
					\item[-] Also optimized for mobile view
				\end{list2}
				\medskip
				\item \emph{Developed} \textbf{\textsf{BlueHat}} -- A full fledged chat server that runs on my \emph{own protocol}.
				\begin{list2}
					\item[-] Implemented my own \emph{concurrency handling mechanism} with a \emph{unique buffer management}
					\item[-] Developed primarily for my high school project, and was awarded the \emph{“Best Project of the Year”}
					\item[-] It was used by many students at school.
				\end{list2}
			\end{list2} 

		 \section{\sc Opensource \\Contributions}
		 	\begin{list1}
				\item[] My opensource contributions are available in GitHub -- \href{http://github.com/aarvay} {http://github.com/aarvay}. It includes some of my other small projects.
			\end{list1}
				
		 \section{\sc Co-Curricular \\Activities}
			\begin{list2}
				\item An elite member of \textbf{\textsf{GLOSS}} \emph{(GNU Linux \& Open Source Society)} at my university. Roles include co-ordinating, and conducting sessions on various fields in FOSS, including Linux customizations and Hackathons.
				\medskip
				\item \emph{Founding member} of the Theoretical Computer Science Club at SASTRA. It aims at encouraging students to paricipate in Programming events and help them with other related theoretical works.
			\end{list2}
		
		\section{\sc Other \\Activities}
			\begin{list2}
				\item A recognized \emph{Mrudangam artist} (An Indian Percussion Instrument)
				\begin{list2}
					\item[-] Performed in over 300 concerts
					\item[-] Winner in numerous competitions
				\end{list2}
				\medskip
				\item A self-taught guitar player.
				\medskip
				\item A street magician - Performed on various occasions.
			\end{list2}
		
		\section{\sc Skill Set}
			\begin{list1}
				\item[] \emph{Programming Languages}
				\begin{list2}
					\item[-] C, C++, Java, Visual Basic, J2ME, Pascal, Ruby, Python
				\end{list2}
				\item[] \emph{Scripting Languages}
				\begin{list2}
					\item[-] BASH
				\end{list2}
				\item[] \emph{Web Technologies}
				\begin{list2}
					\item[-] HTML, CSS, Javascript, PHP (Zend,Yii), Ruby on Rails, AJAX, jQuery
				\end{list2}
				\item[] \emph{DBMS}
				\begin{list2}
					\item[-] MySQL, SQLlite, Oracle, SQL Server, NoSQL(MongoDB)
				\end{list2}
			\end{list1}
	\end{resume}
\end{document}